%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Connect 4 with AI} % Title(s)
    {} % Project
    {}
    {\textcolor{link}{\href{https://github.com/ad3ldev/Connect4-with-AI}{Link}}} % Link
    {
      \begin{cvitems} % Description(s) of project
        \item {Developed a Connect 4 desktop game using Python, with an AI opponent.}
        \item {Implemented MiniMax algorithm with a tree of a preferred max depth of K=5 to act as the AI opponent.}
        \item {Improved MiniMax using alpha-beta pruning to increase its speed by  2,000\% at a depth of K=6, and 600\% at a depth of K=5.}
        \item {Designed a friendly GUI using PyGame that lets the player choose which type of MiniMax algorithm they want, and the depth of the algorithm (K).}
      \end{cvitems}
    }
    
%---------------------------------------------------------

  \cventry
    {REST Countries API} % Title
    {} % Project
    {}
    {\textcolor{link}{\href{https://ad3ldev.github.io/rest-countries-api}{Link}}}% Link
    {
      \begin{cvitems} % Description(s) of project
        \item {Solved a challenge found on \textcolor{link}{\href{https://frontendmentor.io}{frontendmentor.io}} to create a website that shows all the countries of the world and their information.}
        \item {Took advantage of RESTful API calls to ”https://restcountries.com/v2/all” to get data, and cache them to use for search.}
        \item {Reverse-engineered the design given using React and created components for each design element.}
      \end{cvitems}
    }
    
%---------------------------------------------------------

  \cventry
    {TicTacToe} % Title
    {} % Project
    {}
    {\textcolor{link}{\href{https://aadela-tictactoe-web.netlify.app/}{Link}}}% Link
    {
      \begin{cvitems} % Description(s) of project
        \item {Designed a traditional TicTacToe game that can be played against an AI or in a 2-player mode.}
        \item {Implemented the minimax algorithm with various degrees of difficulty to allow the player to choose the depth of the search tree of the AI.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
